\begin{thebibliography}{99999}
\phantomsection
\singlespace\normalsize

\bibitem{SMResearch} Global Social Media Research 2016. \url{http://www.smartinsights.com/social-media-marketing/social-media-strategy/new-global-social-media-research/} accessed on April 2016.

\bibitem{pagefair} The 2015 Ad  Blocking Report, August 2015. \url{https://pagefair.com/blog/2015/ad-blocking-report/} accessed on April 2016.

\bibitem{digitalInfo} 30+ Amazing YouTube Facts. \url{http://www.digitalinformationworld.com/2015/04/30-interesting-facts-about-youtube-infographic.html} accessed on April 2016.

\bibitem{zephoria} The Top 20 Valuable Facebook Statistics. \url{https://zephoria.com/top-15-valuable-facebook-statistics/} accessed on April 2016.

\bibitem{bigdata} Kim H.Pries, Robert Dunnigan. \textit{BIG DATA ANALYTICS. A Practical Guide for Managers.} 2014.

\bibitem{POSTNOTE460} Social Media and Big Data, POSTNOTE, Number 460, March 2014.

\bibitem{bdtech} Min Chen, Shiwen Mao, Yin Zhang, Victor C.M.Leung. \textit{Big Data Related Technologies, Challanges and Future Prospects}. Springer, 2014.

\bibitem{machinelearningdef} Alex Smola and S.V.N. Vishwanathan, INTRODUCTION TO MACHINE LEARNING, Revision 252, October 2010.

\bibitem{machinetypes} Aaron Hertzmann and David Fleet, Machine Learning and Data Mining. Lecture Notes. February 2012.

\bibitem{nltk} Image extracted from \url{http://www.nltk.org/book/ch06.html#fig-supervised-classification} accessed on June 2016.

\bibitem{bayesian} Naive-Bayes Classification Algorithm. \url{http://software.ucv.ro/~cmihaescu/ro/teaching/AIR/docs/Lab4-NaiveBayes.pdf} accessed on June 2016.

\bibitem{k-neighbor} Javier B´ejar, K-nearest neighbours. 2012-2013. \url{http://www.cs.upc.edu/~bejar/apren/docum/trans/03d-algind-knn-eng.pdf} accessed on June 2016.

\bibitem{typescluster} Imagine extracted from \url{http://slideplayer.com/slide/5220241/} accessed on June 2016.

\bibitem{wikicategory} Image extracted from the source: KRZYSZTOF SUCHECKI, ALKIM ALMILA AKDAG SALAH, CHENG GAO, ANDREA SCHARNHORST, EVOLUTION OF WIKIPEDIA’S CATEGORY STRUCTURE. March 2012.

\bibitem{sas} Hadoop. What is it and why does it matter? \url{http://www.sas.com/en_us/insights/big-data/hadoop.html#hadoopusers} accessed on April 2016.

\bibitem{hdfsFigure} Hadoop Architecture image extracted from \url{http://www.rosebt.com/blog/hadooparchitecture-and-deployment} accessed on April 2016.

\bibitem{blog} Hadoop Demystified. \url{http://blog.raremile.com/hadoop-demystified/} accessed on April 2016.

\bibitem{rosebt} Hadoop Architecture and Deployment. \url{http://www.rosebt.com/blog/hadooparchitecture-and-deployment} accessed on April 2016.

\bibitem{tableHadoop} Table RDBMS compared to MapReduce extracted from book: Tom White. \textit{Hadoop: The Defeitive Guide.} O'Reilly, 2015.

\bibitem{CAP} CAP theorem. \url{https://en.wikipedia.org/wiki/CAP_theorem} accessed on April 2016.

\bibitem{AP} Robert Greiner. \textit{CAP Theorem: Revisited.} \url{http://robertgreiner.com/2014/08/cap-theorem-revisited/} accessed on April 2016.

\bibitem{cyber}\textit{The Importance of Bloggers to PR (and How Best to Woo Them).} \url{http://www.cyberalert.com/blog/index.php/the-importance-of-bloggers-to-pr-and-how-best-to-woo-them/} accessed on April 2016.

\bibitem{mongodb-adv} MongoDB Official Web Page. \textit{Document Databases} accessed on May 2016.

\bibitem{survey} Vishal Gupta and Gurpreet S. Lehal, A Survey of Text Mining Techniques and Applications, JOURNAL OF EMERGING TECHNOLOGIES IN WEB INTELLIGENCE, VOL. 1, NO. 1, AUGUST 2009. 

\bibitem{sufix}  M.F. Porter, An Algorithm for Suffix Stripping, Program, vol. 14, no. 3, pp. 130-137, 1980.

\bibitem{MI} Ms. Anjali Ganesh Jivani, A Comparative Study of Stemming Algorithms, Anjali Ganesh Jivani et al, Int. J. Comp. Tech. Appl., Vol 2 (6), 1930-1938, ISSN:2229-6093.

\bibitem{stemming} C.Ramasubramanian and R.Ramya, Effective PreProcessing Activities in Text Mining using Improved Porter's Stemming Algorithm, International Journal of Advanced Research in Computer and Communication Engineering Vol. 2, Issue 12, December 2013, ISSN (Online) : 2278-1021. 

\bibitem{truncat-stemm} Harman Donna, How effective is suffixing?
Journal of the American Society for Information Science, 1991; 42, 7-15 7.

\bibitem{whypostgres} Josh Berkus, LWN.net. "Big data" features coming in PostgreSQL 9.5. August 2015. \url{https://lwn.net/Articles/653411/} accessed on May 2016. 

\bibitem{postgresweb} PostgreSQL Official Web Page. PostgreSQL 9.1.22 Documentation. Chapter 11. Indexes. \url{https://www.postgresql.org/docs/9.1/static/indexes-types.html} accessed on May 2016.

\bibitem{marketing} Principles of Marketing saylor.com
\bibitem{prodcutFigure} Figute 
\bibitem{stages} QuickMBA. \textit{The Product Life Cycle.} \url{http://www.quickmba.com/marketing/product/lifecycle/} accessed on May 2016.

\end{thebibliography}
