\section*{Introduction}

\pagenumbering{arabic}
\setcounter{page}{13}
\phantomsection

Nowadays, over 31\% of total population are active social media users, \cite{SMResearch}. That's why social media are increasingly being used as an information source. Social networking, blogs, dsiscussion forums, wikis, photo-sharing, and video-sharing sites are a few examples of social media chanells. Beside information that thesee channels provide users have the possibility to express their opinion regarding one post by sharing and posting comments.

Throughout the time, social media, became an important business instrument. This not only allows you to better target your audience but it also helps you understand the specific needs of your customer base. Because social media functions best in real-time, it gives you instant access to feedback from your customers. 

In the last years placing advertising content on the most popular social media channels was a strong marketing tool used by companies. Now, with the growing number of users that has ad blocks, software programs that prevent ads from being shown on websites, the impact of marketing approach decreased considerably. According to data from Adobe and PageFair, adoption of desktop ad blockers has risen steadily in recent years, from approximately 21 million users in 2010 to more than 181 million users in January 2015, \cite{pagefair}. This number is expected to continue to rise with the ad-blocking functionality that was just released. 

In this contex \textbf{blogs} have emerged as an influential new media outlet for PR stories and product reviews. Readers trust third-party blog posts about a company more than statemts from the company itself. Thus, blog posts improve the image of a brand and increase its awareness. A placement in a blog that pecializes on a speific topic guarantees an interested audience. This audience of an influential blogger can reach up to 2 millions views in less than 16 hours. Bloggers also have a level of trust and interest much bigger that simple advertising banners. 

The big number of users that are doing video blogs on different themes, leads to problem of finding the suitable bloggers by the interested parts. Lexical analysis of social media can reveal bloggers and social media influencers by using text mining tools. An important text mining algorithm that can handle working with data from social media is information extraction. It is the task of automatically extracting structured information from unstructured and/or semi-structured data.

The problem researched in this work is regarding the methods of reach bloggers and influencers in soial media. As a chanell of social media is considered - Youtube. Since YouTube is the number one place for creating video blogs, with can be an incredibly powerful social media marketing tool. The goal is to create a tool which will find the most influence bloggers accroding to a field of interest or a keyword. The main problem that Finduber will resolve is: Given that you have 1.5 million YouTubers and a company that makes soap, how do you find the right ones?


The application would consist from two console applications that are ran in backend and a web page. Backend applications aim to create a lexical based search engine as well as a database optimization. Web application is created to show the results to users.

\clearpage